\\fontsize{12pt}{3pt}\\selectfont \\textbf{\\textit{Submitted to the journal Ecological Monographs. Manuscript type: Article}}

### 2023-05-22 manuscript/manuscriptRW.Rmd
add table 1 to manuscript folder and change path in the manuscript

```{r tableModels, echo=FALSE,  message=FALSE, warning=TRUE}
library(knitr)
modelDF <- readr::read_csv(here::here("data", "modelsDescription.csv"))
modelDF$Sampling <- NULL

>>>>

```{r tableModels, echo=FALSE,  message=FALSE, warning=TRUE}
library(knitr)
modelDF <- readr::read_csv(here::here("manuscript", "modelsDescription.csv"))
modelDF$Sampling <- NULL
